## SPSS to R
=================

[![Build Status](https://travis-ci.org/lebebr01/SPSStoR.svg?branch=master)](https://travis-ci.org/lebebr01/SPSStoR)
  
A set of functions that takes *SPSS* syntax as input and outputs *R* commands 
to do the same analysis or data management tasks.

## Current Features
===============
* Read in Data
    * Get for sav files
* Data Manipulation
    * Sort Cases
* Descriptives
    * Aggregate
    * Correlations
    * Crosstab
    * Descriptives
    * Frequencies
    * Graphics    
* Models
    * One sample t-test
    * Independent sample t-test
    * One-way ANOVA




## Upcoming Features
=================
* More Get commands to read in csv, txt, etc.
* Dataset commands
* Value Labels
* Further arguments for descriptives
* Modeling functions
    + t-test (two sample with cut score and paired)
    + analysis of variance - more complicated designs
    + regression
    + generalized models
* if else statements
* Examine

## Installing Function
===================
```{r install, eval = FALSE}
library(devtools)
install_github("SPSStoR", username = "lebebr01")
library(SPSStoR)
```

## Examples
=========
### Multiple commands
------------------
```{r multiple}
# Multiple commands in one
spss_to_r(system.file("SPSSsyntax", "getDescExamp.txt", package = "SPSStoR"))

```


### Aggregate Example
-----------------------
```{r agg, warning = FALSE, message = FALSE}
  spss_to_r(system.file("SPSSsyntax", "aggregateExamp.txt", package = "SPSStoR"))
```

### Correlation Example
-------------------------
```{r corr, warning = FALSE, message = FALSE}
  spss_to_r(system.file("SPSSsyntax", "correlationsExamp.txt", package = "SPSStoR"))
```

### Crosstab Example
----------------------
```{r crosstab, warning = FALSE, message = FALSE}
  spss_to_r(system.file("SPSSsyntax", "crosstabExamp.txt", package = "SPSStoR"))
```

### Sort Cases Example
-----------------------
```{r sortcase, warning = FALSE, message = FALSE}
  spss_to_r(system.file("SPSSsyntax", "sortCasesExamp.txt", package = "SPSStoR"))
```

### Descriptives Example
-------------------------
```{r desc, warning = FALSE, message = FALSE}
  spss_to_r(system.file("SPSSsyntax", "descriptivesExamp.txt", package = "SPSStoR"))
```

### t-test Examples
--------------------------
```{r ttest}
# t-test one-sample
  spss_to_r(system.file("SPSSsyntax", "ttestOneSampExamp.txt", package = "SPSStoR"))
# Independent t-test example
  spss_to_r(system.file("SPSSsyntax", "ttestTwoSampValExamp.txt", package = "SPSStoR"))
  
```

### Get Command Example
-------------------
```{r get}
  spss_to_r(system.file("SPSSsyntax", "getExamp.txt", package = "SPSStoR"))
```

### Graphics
----------------
```{r graphics}
  spss_to_r(system.file("SPSSsyntax", "graphExamps.txt", package = "SPSStoR"))
```

### Frequencies
---------------
```{r frequencies}
  spss_to_r(system.file("SPSSsyntax", "frequenciesExamp.txt", package = "SPSStoR"))
```



