SPSS to R
=================
  
A set of functions that takes *SPSS* syntax as input and outputs *R* commands 
to do the same analysis or data management tasks.

Current Features
===============
* Aggregate
* Correlations
* Crosstab
* Sort Cases
* Descriptives


Upcoming Features
=================
* Master SPSStoR function
* Value Labels
* Further arguments for above current features
* Modeling functions
    + t-test
    + analysis of variance
    + regression
    + generalized models
* if else statements
* graphics

Installing Function
===================
```{r install, eval = FALSE}
library(devtools)
install_github("SPSStoR", username = "lebebr01")
library(SPSStoR)
```

Aggregate to R Example
======================
```{r setup, echo = FALSE}
  setwd("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/")
```

```{r agg, warning = FALSE, message = FALSE}
 library(SPSStoR)
  aggregate_to_agg("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/aggregateExamp.txt", 
                   syntax = "data.table")
  aggregate_to_agg("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/aggregateExampNoBreak.txt", 
                   syntax = "data.table")
  aggregate_to_agg("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/aggregateExampNoBreakNoOutfile.txt", 
                   syntax = "data.table")
  aggregate_to_agg("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/aggregateExampNoOutfile.txt", 
                   syntax = "data.table")
```

Correlation to R Example
=========================
```{r corr, warning = FALSE, message = FALSE}
  correlations_to_cor("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/correlationsExamp.txt")
```

Crosstab to R Example
======================
```{r crosstab, warning = FALSE, message = FALSE}
  crosstabs_to_table("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/crosstabExamp.txt")
```

Sort Cases to R Example
=======================
```{r sortcase, warning = FALSE, message = FALSE}
  sortcases_to_order("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/sortCasesExamp.txt")
  sortcases_to_order("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/sortCasesExamp2.txt")
```

Descriptives to R Example
========================
```{r desc, warning = FALSE, message = FALSE}
  descriptives_to_descmat("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/descriptivesExamp.txt")
  descriptives_to_descmat("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/descriptivesExampAll.txt")
```
