SPSS to R
=================
  
A set of functions that takes *SPSS* syntax as input and outputs *R* commands 
to do the same analysis or data management tasks.

Current Features
===============
* Aggregate
* Correlations
* Crosstab
* Sort Cases
* Descriptives
* One sample t-test
* Independent sample t-test
* Get for sav files
* Master SPSStoR function


Upcoming Features
=================
* More Get commands to read in csv, txt, etc.
* Dataset commands
* Value Labels
* Further arguments for above current features
* Modeling functions
    + t-test (two sample with cut score and paired)
    + analysis of variance
    + regression
    + generalized models
* if else statements
* graphics

Installing Function
===================
```{r install, eval = FALSE}
library(devtools)
install_github("SPSStoR", username = "lebebr01")
library(SPSStoR)
```

Aggregate to R Example
-----------------------
```{r setup, echo = FALSE}
  setwd("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/")
```

```{r agg, warning = FALSE, message = FALSE}
 library(SPSStoR)
  spss_to_r("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/aggregateExamp.txt")
  spss_to_r("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/aggregateExampNoBreak.txt")
  spss_to_r("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/aggregateExampNoBreakNoOutfile.txt")
  spss_to_r("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/aggregateExampNoOutfile.txt")
```

Correlation to R Example
-------------------------
```{r corr, warning = FALSE, message = FALSE}
  spss_to_r("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/correlationsExamp.txt")
```

Crosstab to R Example
----------------------
```{r crosstab, warning = FALSE, message = FALSE}
  spss_to_r("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/crosstabExamp.txt")
```

Sort Cases to R Example
=======================
```{r sortcase, warning = FALSE, message = FALSE}
  spss_to_r("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/sortCasesExamp.txt")
  spss_to_r("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/sortCasesExamp2.txt")
```

Descriptives to R Example
========================
```{r desc, warning = FALSE, message = FALSE}
  spss_to_r("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/descriptivesExamp.txt")
  spss_to_r("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/descriptivesExampAll.txt")
```

One Sample T-test Example
=========================
```{r ttestOS}
  spss_to_r("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/ttestOneSampExamp.txt")
  
```

Indpendent Sample T-test Example
===============================
```{r ttestIS}
  spss_to_r("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/ttestTwoSampValExamp.txt")
```

Get Command Example
===================
```{r get}
  spss_to_r("C:/Users/e520062/Dropbox/SPSStoR/SPSSsyntax/getExamp.txt")
```

